%% Title
\titlepage[Imperial College London\\Department of Physics]%
{A dissertation submitted to Imperial College London\\
  for the degree of Doctor of Philosophy}

\input{cpright}

%% Abstract
\begin{abstract}%[\smaller \thetitle\\ \vspace*{1cm} \smaller {\theauthor}]
  %\thispagestyle{empty}
  The search for BSM physics is one of the primary objectives of the LHC.
  This thesis describes the~$\alpha_{\text{T}}$~search for supersymmetry using a dataset of $12.9\,\text{fb}^{-1}$ 
  collected during the 2016 proton-proton runs by the CMS detector. The search uses a final state 
  containing significant hadronic activity in the form of jets, missing energy, and no leptons or photons.
  Dedicated dimensionless variables ensure that backgrounds with fake missing energy are mitigated. A detailed description 
  is given of the selections used to mitigate backgrounds while maintaining acceptance to a wide range of signal models 
  and of the techniques used to ensure a robust determination of the residual backgrounds and systematic uncertainties.
  No evidence for BSM physics is observed and simplified models are therefore used to interpret the results of 
  the search. Stringent new limits are placed on a range of supersymmetric topologies and a procedure
  to allow the search to be re-interpreted for any BSM physics model is presented.

  Additionally, the upgrade of the Level-1 trigger jet and energy sum algorithm
  is studied. The upgraded trigger hardware is exploited to ensure effective performance in conditions exceeding 
  the design specification of the LHC.

\end{abstract}


%% Declaration
\begin{declaration}
I, the author of this thesis, hereby declare the work contained in this 
document to be my own. All figures labelled `CMS' are sourced directly from CMS publications, 
including those produced by the author and have been referenced as such 
in the figure caption. Figures marked `CMS Preliminary' are sourced from an unpublished 
or preliminary public document. All figures and studies taken from external sources are referenced appropriately 
throughout this document.

The studies for the trigger upgrade presented in Chapter~\ref{cha:triggerUpgrade} are 
the result of my own work carried out within the UK CMS Trigger group. I have
been a major contributor to all areas of the $\alpha_\text{T}$ 
analysis presented in Chapters~\ref{cha:alphat}, \ref{cha:backgroundPrediction}, 
and \ref{cha:statisticalResults} as part of the Imperial College London and CERN SUSY groups.
The aspects of the search which were my primary responsibility are
the inclusion of the \mht~shape described in Section~\ref{sec:syst-on-shape} 
and the statistical interpretations described in Chapter~\ref{cha:statisticalResults}.
Finally, I have carried out the work to facilitate re-interpretations described in 
Chapter~\ref{cha:simplifiedLikelihood} with a CMS collaborator.
%  \vspace*{1cm}
  \begin{flushright}
    Matthew Citron
  \end{flushright}
\end{declaration}


%% Acknowledgements
\begin{acknowledgements}

Many thanks to all the people I have worked with over the course of the last 3 and a half years.
In particular, thanks to Rob Bainbridge for his constant help and support and to my 
\alphat colleagues Mark Baber, Shane Breeze, Stefano Casasso, Adam Elwood, Lucien Lo, Christian Laner, Bjoern Penning
and Alex Tapper. Thanks also to Nick Wardle and Jad Marrouche for all their statistical and L1 jet
related help and to my supervisor Oliver Buchmueller for his guidance
throughout my PhD. I'm grateful to my fellow PhD students, Louie Corpe, Adinda de Wit, Lucien Lo and Federico Redi
for many fruitful discussions. Finally, thanks to my parents for all their patience, support and proofreading.

\end{acknowledgements}


%% Preface
%\begin{preface}
% Insert preface here...
%\end{preface}

%% ToC
\tableofcontents

\listoffigures
\listoftables
%% Strictly optional!
% \frontquote%
%   {I struggled with some demons\\ They were middle class and tame}
%   {Leonard Cohen}
